The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 SI.tex
Add analytical solution to anisotropy

\subsection{Comparing dielectric anisotropy}
\label{ssec:aniso}
The dielectric anisotropy $\eta$ proposed in the main text is also
applied to other dimensions. Similar to the case of 2D and bulk
layered materials, $\epsilon$ is used to compare the anisotropy when
the material is periodic in all dimensions (bulk covalent materials),
while the polarizability $\alpha$ is used for reduced dimensional
materials.

@@

\subsubsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
\label{sssec:aniso-1}

>>>>

\subsection{Comparing dielectric anisotropy}
\label{ssec:aniso}
\subsubsection{Choice of materials}
\label{sssec:aniso-1}
The dielectric anisotropy $\eta$ proposed in the main text is also
applied to other dimensions. Similar to the case of 2D and bulk
layered materials, $\epsilon$ is used to compare the anisotropy when
the material is periodic in all dimensions (bulk covalent materials),
while the polarizability $\alpha$ is used for reduced dimensional
materials.

@@

\subsubsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
\label{sssec:aniso-2}
In this section we give an analytical explanation for the separation
between the dielectric anisotropy indices of 2D and their bulk
counterparts. From main text Eqs. \ref{main-eq:alpha-para-def},
\ref{main-eq:alpha-perp-def} and \ref{main-eq:anisotropy},
$\eta_{\mathrm{Bulk}}$ of a bulk layered material is expressed as:
\begin{equation}
  \label{eq:eta-bulk}
  \begin{aligned}[t]
    \eta_{\mathrm{Bulk}} &= \frac{\varepsilon_{\mathrm{Bulk}}^{\perp}}
    {\varepsilon_{\mathrm{Bulk}}^{\parallel}}\\
    &= \frac{1}{\left(1 + {\displaystyle
          \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0}L_{\mathrm{Bulk}}}}\right)
      \left(1 - {\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0}L_{\mathrm{Bulk}}}} \right)}\\
    &= \frac{1}{ \left[1-\left( {\displaystyle
            \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
        \left(
          {\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0}
            L_{\mathrm{Bulk}}}} \right) \right]
      \left[ 1 + \left(
          {\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0}
            L_{\mathrm{Bulk}}}} \right)\right]
    }
    % &= \frac{\left({\displaystyle \frac{\varepsilon_{0}L_{\mathrm{Bulk}}}{\alpha^{\parallel}_{\mathrm{Bulk}}}}\right)^{2}}
    % {\left({\displaystyle \frac{\varepsilon_{0}L_{\mathrm{Bulk}}}{\alpha_{\mathrm{Bulk}}^{\parallel}_{\mathrm{2D}}}}\right)^{2}    
      % -\left({\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
      % \left({\displaystyle \frac{\varepsilon_{0} L_{\mathrm{Bulk}}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
      % + \left({\displaystyle \frac{\varepsilon_{0} L_{\mathrm{Bulk}}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
      % -\left({\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)}
  \end{aligned}
\end{equation}
Name take the fact that
$\alpha_{\mathrm{Bulk}}^{\parallel} \approx
\alpha^{\parallel}_{\mathrm{2D}}$ (main text Figure
\ref{main-fig-4}b), we name
$\alpha_{\mathrm{Bulk}}^{\parallel} /\epsilon_{0}L_{\mathrm{Bulk}}
\approx \alpha_{\mathrm{2D}}^{\parallel}/
\epsilon_{0}L_{\mathrm{Bulk}}$ as $\gamma$. Furthermore we name
$\alpha_{\mathrm{Bulk}}^{\perp}/\alpha_{\mathrm{Bulk}}^{\parallel}$ as
$\hat{\eta_{\mathrm{2D}}}$, that
$\hat{\eta}_{\mathrm{2D}} =
\alpha_{\mathrm{Bulk}}^{\perp}/\alpha_{\mathrm{Bulk}}^{\parallel} \geq
\alpha_{\mathrm{2D}}^{\perp}/\alpha_{\mathrm{2D}}^{\parallel}=\eta_{\mathrm{2D}}$,
and Eq. \ref{eq:eta-bulk} is reduced to:
\begin{equation}
  \label{eq:eta-bulk-2}
  \eta_{\mathrm{Bulk}} = \frac{1}{(1 - \hat{\eta}_{\mathrm{2D}} \gamma) (1 + \gamma)}
\end{equation}
The minimal value for $\eta_{\mathrm{Bulk}}$ when $\gamma>0$ is obtained by solving:
\begin{equation}
  \label{eq:eta-bulk-min}
  \frac{\partial \eta_{\mathrm{Bulk}}}{\partial \gamma}
  = \frac{2 \hat{\eta}_{\mathrm{2D}} \gamma + \hat{\eta}_{\mathrm{2D}} - 1}
  {(\gamma+1)^{2}(1 - \hat{\eta}_{\mathrm{2D}} \gamma)^{2}} = 0
\end{equation}
which gives that
$\eta_{\mathrm{Bulk}} \geq \frac{4
  \hat{\eta}_{\mathrm{2D}}}{(\hat{\eta}_{\mathrm{2D}} + 1)^{2}}$,
where the minimal value is taken at
$\gamma = \frac{1}{2}(\frac{1}{\hat{\eta}_{\mathrm{2D}}} - 1)$. Since
$\frac{4 \hat{\eta}_{\mathrm{2D}}}{(\hat{\eta}_{\mathrm{2D}} +
  1)^{2}}$ monotonically increases when
$0 < \hat{\eta}_{\mathrm{2D}} < 1$, we get the comparison between the
dielectric anisotropy indices between 2D materials and their bulk
counterparts:
\begin{equation}
  \label{eq:aniso-final}
\eta_{\mathrm{Bulk}} \geq \frac{4
  \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}} + 1)^{2}} \geq
\eta_{\mathrm{2D}} 
\end{equation}
Since $\gamma$ is actually $2r_{0}^{\parallel}/L_{\mathrm{Bulk}}$, the
ratio between the in-plane screening length $r_{0}^{\parallel}$ and
inter-plane distance $L_{\mathrm{Bulk}}$, and in general
$r_{0}^{\parallel} \gg L_{\mathrm{Bulk}}$, we can conclude that the
case when $\eta_{\mathrm{Bulk}} = \eta_{\mathrm{2D}}$ only happens
when $\eta_{\mathrm{2D}}$ is much smaller than 1. Therefore the
separation between the 2D and 3D regimes in the Figure
\ref{main-fig:aniso} is explained.

\section{}

### 2018-11-15 paper.tex
Add analytical solution to anisotropy

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
of corresponding 2D layer (details see Supplementary Section SXX
\todo{note}), which is the basis for the separation of bulk and 2D
regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
we also superimpose the dielectric anisotropy indices $\eta$ of common
semiconducting materials in other dimensions (details see
Supplementary Section ) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}

>>>>

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
index of corresponding 2D layer (details see Supplementary Section
\ref{SI-sssec:aniso-2}), which is the basis for the separation of bulk
and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For
comparison, we also superimpose the dielectric anisotropy indices
$\eta$ of common semiconducting materials in other dimensions (details
see Supplementary Section \ref{SI-sssec:aniso-1}) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}
